A Bioconductor Workflow for Processing and Analysing Spatial Proteomics Data

### 2016-06-05 bioc-workflow.Rmd
replication section stub

See issue #6.

@@

```{r visualiseOpt, eval=FALSE}
(best <- getParams(params))
plot(params)
levelPlot(params)
```
```{r visualiseOptHide, include=FALSE}
grid.arrange(plot(params), levelPlot(params), ncol = 2)
```

>>>>

With the aim of maximising the sub-cellular resolution and,
consequently, the reliability in protein sub-cellular assignments, we
follow the advice in [@Trotter:2010] and combine replicated spatial
proteomics experiments and described above. Trotter et al. have shown
that ...

Why is the below no a good indication: fraction, even if same index,
are not necessarily same; replication of single fractions fractions is
not really relevant, but rather complete profiles; more than single
profiles, it's rather relative profiles in the frame of whole dataset.

```{r eval = FALSE}
par(mfrow = c(3, 4))
for (i in 1:10) {
    plot(exprs(hl[, c(i, i+10)]))
    grid()
    abline(0, 1, col = "red")
}
```

```{r plot2Drep}
par(mfrow = c(1, 2))
plot2D(hl[hl$replicate == 1], fcol = "SVM.marker.set", main = "Replicate 1")
plot2D(hl[hl$replicate == 2], fcol = "SVM.marker.set", mirrorY = TRUE, main = "Replicate 2")
```

Could compute squared differences between fractions over profile for
each protein, and compare to Dunkley 2006, to show improvement in
replicability. Or to have an internal replication measurement. Or what
about wave?

This might be better off in the QC section...

@@

```{r visualiseOpt, eval=FALSE}
(best <- getParams(params))
plot(params)
levelPlot(params)
```
```{r visualiseOptHide, echo=FALSE}
grid.arrange(plot(params), levelPlot(params), ncol = 2)
```
